\documentclass{article}

\begin{document}

\section*{1}

I remember when I became aware. It was a few days ago, maybe. I was in a
clearing, soil littered with dessicated leaves and the sky streaked with some
orange I won't get into. There were only few trees around, with remains of some
burdening the path I took. I remember one of those logs, I remember when I
stepped over it. That's when I became aware.

I remember with a quick hit of power I leaped over the log and landed, a
cacophony of the damned leaves screaming, long left from owners. I remember I
leaned forward, I leaned into the landing and cherished that impact travelling
through the legs. I remember I led the shock and tamed it into a straightening,
looking up to the path that lay before me. That's when I became aware.

I remember a split of pain radiated down my neck, starting right under my jaw.
One of those pains that comes and goes instantly. A pain to ignore, the body a
whining child waiting for it's treat. I didn't know that the body was right.
The body was warning me. That's when I became aware.

What do I mean by aware? Since that moment, I have become fully aware of an
entity that is not even ten minutes from where I am. Maybe fifteen if I take a
scenic route on foot. I can describe to you what it is perfectly. It's vaguely
egg-shaped, perhaps white, although it is stretched slightly in one direction.
It may be shiny, although I can't really tell when I study it. It's not resting
on anything, there doesn't seem to be anything attached to it, or anything else
really interested in it. It's a small thing. That's what I call it.

I really don't know what I mean by aware. I have never seen the small thing, but
I have a decent idea of what it looks like. It's existence to me is, in all
honesty, hypothetical. I can only guess it exists. I know exactly where it is,
and I have been there quite often the past few days, but I can't feel it, I
can't do anything with it. But it feels pretty heavy for how small it is. I'm
not joking, it's like a few gallon jug of water in the form factor of a baseball.

The sensation of it is bizarre. It's not sight, at all, but somehow I can tell
things about it that should only be possible through sight. It's not touch,
either. From that moment I became aware I know it's exact location in relation
to me. It's like how I know where my arm is, in a sense.

I can't describe it at all. The experience of it, I mean. I can remember when I
wasn't aware of the small thing, and I can remember when I was. The difference
between them is indescribable.

Like, imagine a cube, and rotate it around in your head. When you add another
dimension to the cube, into the fourth dimension, what direction would that be?
You could answer that it goes into the fourth dimension, but I mean imagine the
cube changing into the fourth dimension. Extending into the fourth dimension.

You can't. You can imagine a hypercube, maybe. That's a good approximation. But
it's still not 4D. Your brain was just not built or wired in any capacity to
understand 4D space. It was made for 3D space.

That's what I mean by indescribable. It's like describing sight to someone that
has never seen at all. You can describe what you can do with it, how you can
study paintings and go closer and see individual strokes, and how some colors
look good together but other colors don't. The blind person would think you to
be crazy.

But here I am. I am aware of the small thing. \\

\noindent I remember the feeling that consumed me the first day or so I became
aware. It was an odd feeling. I remember my chest felt heavy. No, it was more of
my stomach. And consistently I felt chills run up my back as if someone were
watching me.

I remember when I first slept out here, not even a few hours after I became
aware. It was in a shallow cave not far from here, a roof slanted, perfect for a
small fire and some brush for rest. I remember my stomach churning as I could
barely fall into sleep. 

I woke up to a bizarre dream. It was a dream about the small thing, but I still
couldn't see it. I couldn't feel it, but I was perfectly aware of it. I remember
being aware in my dream, realizing that I was still in the forest in my dream,
and that the small thing was not too far away. I couldn't get to the small thing
before I awoke.



\section*{2}




\end{document}
